Fractional Types

### 2019-11-23 fracGC/p.tex
intro and figure for languages

The paper includes a number of languages that express different
points. The three most important languages and their relationships are
highlighted in this diagram:
\begin{center}
\input{lang.tikz}
\end{center}

>>>>

The paper includes a number of languages that express different
points. The three most important languages and their relationships are
highlighted in this diagram:
\begin{center}
\input{lang.tikz}
\end{center}
The language $\Pi$ is the base language of type isomorphisms. It is
defined in Sec. 3, and first extended with fractional types in
Sec. 4.4. This extension $\Pi/D$ requires a runtime check to ensure
safe de-allocation. In Sec. 6.2, $\Pi$ is independently extended to
$\Pi/\bullet$ which uses singleton types to keep track of the value of
ancillae. In Sec. 6.3, we show that $\Pi/D$ programs extracted from
$\Pi/\bullet$ are safe without the runtime checks associated with
de-allocation.
